AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-10 publications/iaai21/dora_outlier_detection_iaai.tex
Update results for Earth exp with corrected plots and PAE. #42

\subsubsection{Satellite time series for ground-truth observations.}
We used the full dataset of 6,757 samples to fit the ranking algorithms and
used the independently-labeled set of 113 points in Kenya for evaluation.
Table \ref{fig:faw_results} compares the performance of each ranking 
algorithm by plotting the number of true outliers detected out of the top
$N$ selections. We reported the area under the curve (AUC) in the legend
for each algorithm to give a quantitative comparison of the curves.
Table \ref{tab:faw_results} gives the precision at $N$ where
$N=n_{outlier}=37$. The negative sampling algorithm had the best performance
in both metrics. RX had the lowest precision at $N=n_{outlier}$ while PCA had
the lowest AUC of all algorithms except random.

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for Earth science dataset. }
  \label{tab:faw_results}
  \centering
  \begin{tabular}{cc}
    \hline
    Algorithm & Precision at $N=n_{outlier}$ \\
    \hline
    RX & 0.30 \\
    Random & 0.32 \\
    DEMUD & 0.32 \\
    PCA & 0.35 \\
    Isolation Forest & 0.46 \\
    \textbf{Negative Sampling} & \textbf{0.54} \\
    \hline
  \end{tabular}
\end{table}

>>>>

\subsubsection{Satellite time series for ground-truth observations.}
We used the full dataset of 6,757 samples to fit the ranking algorithms and
used the independently-labeled set of 113 points in Kenya for evaluation.
Table \ref{fig:faw_results} compares the performance of each ranking 
algorithm by plotting the number of true outliers detected out of the top
$N$ selections. We reported the area under the curve (AUC), normalized
by the total number of selections, in the legend
for each algorithm to give a quantitative comparison of the curves.
Table \ref{tab:faw_results} gives the precision at $N$ where
$N=n_{outlier}=37$. The negative sampling algorithm had the best performance
in both metrics. DEMUD, PCA, and PAE tied for the lowest precision at 
$N=n_{outlier}$ while DEMUD and PCA tied for the lowest AUC.

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for Earth science dataset. }
  \label{tab:faw_results}
  \centering
  \begin{tabular}{cc}
    \hline
    Algorithm & Precision at $N=n_{outlier}$ \\
    \hline
    Random & 0.32 \\
    DEMUD & 0.41 \\
    PCA & 0.41 \\
    PAE & 0.41 \\
    RX & 0.43 \\
    Isolation Forest & 0.46 \\
    \textbf{Negative Sampling} & \textbf{0.49} \\
    \hline
  \end{tabular}
\end{table}
